\section*{START HERE: Instructions}

\begin{notebox}
Homework 1 covers topics on overfitting, dropout, backpropagation and neural networks, and convolutional neural networks basics. The homework includes short answer questions, derivation questions, and coding tasks. 
\end{notebox}

\begin{itemize}
\item \textbf{Collaboration policy:} Collaboration on solving the homework is allowed, after you have thought about the problems on your own. It is also OK to get clarification (but not solutions) from books or online resources, again after you have thought about the problems on your own. There are two requirements: first, cite your collaborators fully and completely (e.g., ``Jane explained to me what is asked in Question 2.1''). Second, write your solution {\em independently}: close the book and all of your notes, and send collaborators out of the room, so that the solution comes from you only.  See the Academic Integrity Section on the course site for more information: \url{https://machinelearningcmu.github.io/S24-10707/index.html#7-academic-integrity-policies}

\item\textbf{Late Submission Policy:} See the late submission policy here:\\
\url{https://machinelearningcmu.github.io/S24-10707/index.html#policies}

\item\textbf{Submitting your work:} 

\begin{itemize}

\item \textbf{Gradescope:} For written problems such as short answer, multiple choice, derivations, proofs, or plots, we will be using Gradescope (\url{https://gradescope.com/}).
Please write your solution in the LaTeX files provided in the assignment and submit in a PDF form. Put your answers in the question boxes (between \texttt{\textbackslash begin\{soln\}} and \texttt{\textbackslash end\{soln\}}) below each problem. Please make sure you complete your answers within the given size of the question boxes. \textbf{Handwritten solutions are not accepted and will receive zero credit.} Regrade requests can be made, however this gives the TA the opportunity to regrade your entire paper, meaning if additional mistakes are found then points will be deducted. For more information about how to submit your assignment, see the following tutorial (note that even though the assignment in the tutorial is handwritten, submissions must be typed): \url{https://www.youtube.com/watch?v=KMPoby5g_nE}

\item \textbf{Code submission:} All code must be submitted to a Gradescope autograder named as
``S24 Homework 1: Programming''.  \textbf{If you do not submit your code here, you will not receive any credit for your assignment.} Gradescope grader will be used to check for plagiarism.  Please make sure you familiarize yourself with the academic integrity information for this course.

\end{itemize}

% \item \textbf{Materials:} Download from autolab the tar file (``Download handout"). The tar file will contain all the data that you will need in order to complete this assignment.

\end{itemize}